### 2016-04-19 text/ms.Rmd
Update to do items

<!-- TODO
- [ ] add discussion of uncertainty (CIs) and ML (and incorporating uncertainty into pred.)
- [ ] add back in the roc plot and sentence in the main text
- [ ] rerun the main simulation analysis because the equations of change for the slope
-->

>>>>

<!-- TODO
- [ ] add discussion of uncertainty (CIs) and ML (and incorporating uncertainty into pred.)
- [x] add back in the roc plot and sentence in the main text
- [ ] rerun the main simulation analysis because the equations of change for the slope
- [ ] manually adjusted the labels in figure 4
- [ ] update the magic number get inserted to use the equation that only has the basic model
-->
